\newcommand{\code}[1]{\texttt{#1}}

\subsection{The Problem}
With the original cost model, there is a chance Cozy will output implementations
in which a state variable is highly efficient when a query is run on it, but
is inefficient when a mutator is run. For example, given this specification:

\begin{lstlisting}
    Cats:
        state cats: Set<Cat>

        query countSharedColor(c : Cat)
            assume c in cats;
            len [x | x <- cats, x.colour == c.colour]

        op addCat(c : Cat)
            cats.add(c);
\end{lstlisting}

Cozy will try to output an implementation that is a map from cats to the number
of other cats that have the same colour. This implementation, when being
considered for just the query, is very efficient. However, when the mutator
\code{addCat} is called, the map of cats will have to be updated in two ways:
(1) every existing cat with the same colour as the new cat has to increment their
count by 1, (2) the new cat will have to calculate the number of existing cats
that match its colour. When the number of cats is very large, it can lead to
inefficiency.

By allowing the cost model to also consider the maintenance cost of expressions
with respect to available mutators, Cozy should be able to determine that storing
a map from colours to cats with that colour is much more efficient overall.

\subsection{Overview}
With the original cost model, there were no connections between queries and
mutators. This means that when it is optimizing a query, it is doing so
regardless of how that would affect the performance of the mutators.
The maintenance cost model is provided with information on what mutators (or
\code{op}s) that exists in the specification. It will then calculate the cost to
maintain expressions when there are mutators to be considered.

The maintenance cost of an expression is calculated by changing the original
expression with the mutator, taking the difference between the original and the
changed expressions, and calculating the size of that difference. This also
means that if there are no differences, the maintenance cost is zero.

\subsection{Challenges}
With the cost model being allowed to consider mutators as well as the query
itself, we have to try to optimize for multiple objectives: the queries being
efficient as well as the mutators. Initially, the model replaced max storage
size and true runtime with the sum of the maintenance costs of an expression for
each mutator. Then, it compares the sums calculated from each expression with
each other as the tiebreaker for the asymptotic runtime in the prioritized
ordering.

The problem with this is for cases where there is more than one mutator, for
each expression, there's a chance that it has a different maintenance cost
depending on the mutator that was used on it. This can lead to very confusing
results, as we don't know which maintenance cost is more important, and summing
them doesn't properly convey that information.

To tackle this problem, we added an unprioritized ordering to the cost model.
Opposite to the prioritized ordering, this ordering is used when we don't know
which metric is more important than another. The unprioritized order compares
the maintenance costs of two expressions for each op separately, then check the
comparisons to make sure that they are consistent or ambiguous. This change
allowed the cost model to more properly convey that different mutators can give
different maintenance costs to expressions.

However, with the addition of the maintenance cost, the cost model has become
better at picking out ambiguity between two expressions. An example is for bag
storage, Cozy will be able to find examples where the maintenance cost of an
expression is different depending on what is currently in the bag and which
mutator is being considered.

Furthermore, because Cozy is comparing the maintenance costs of the expressions
for each mutator separately, there is a significant increase in solver calls.
This has made the maintenance cost model much slower than the original, thus
preventing Cozy from finding some solutions that the original could given the
same amount of time.
